---
title             : "EDLD 610 Final Project"
shorttitle        : "Cool Title Name here"

author: 
  - name          : "Brock Rowley"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Behavioral Research & Teaching (BRT)
                    175 Lokey Education 5262 
                    University of Oregon
                    Eugene, OR, 97403-5262"
    email         : "brockr@uoregon.edu"
  - name          : "Kyle Reardon"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"


authornote: |
  Brock Rowley is a Senior Research Associate at Behavioral Research and Teaching (BRT) in the Education Methodolgy, Policy, and Leadership in the Coledge of Education. 
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter Kyle's (author) note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Final Paper

Hello Kyle,
Looking forward to working with you on this project. Feel free to invite the person you were talking about in class?? as the third member of our crew. 
All the best,
Brock

## The final project must:

(a) be a reproducible and dynamic APA manuscript produced with R Markdown, via
the {papaja} package and include references to the extant literature; 
(b) be housed on GitHub, with contributions from all authors obvious;
(c) demonstrate moving data from its raw “messy” format to a tidy data format
through the R Markdown file, but not in the final document;
(d) include at least two exploratory data visualizations, and
(e) include at least summary statistics of the data in tables, although fitted
models of any sort are an added bonus (not literally, there are not extra points
for fitting a model).

## The points for the final project are broken down as follows: 
### Writing (abstract, intro, methods, results, discussion, references)

* 30 points(25%) Document is fully reproducible and housed on GitHub 
* 25 points (21%) Demonstrate use of inline code 
* 5 points (4%) Demonstrate tidying messy data 
* 30 points (25%) Two data visualizations 
* 20 points(10 points each) (17%) Production of at least one table (of summary
  statistics or model results)
* 10 points (8%)