---
title             : "EDLD 610 Final Project"
shorttitle        : "Cool Title Name here"

author: 
  - name          : "Brock Rowley"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Behavioral Research & Teaching (BRT)
                    175 Lokey Education 5262 
                    University of Oregon
                    Eugene, OR, 97403-5262"
    email         : "brockr@uoregon.edu"
  - name          : "Kyle Reardon"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"


authornote: |
  Brock Rowley is a Senior Research Associate I at Behavioral Research and
  Teaching (BRT) and Co-Director of the Admin Licensure Program in the Education
  Methodolgy, Policy, and Leadership in the Coledge of Education at the
  University of Oregon.


  Kyle Reardon (M.A. Special Education) is a doctoral candidate at the
  University of Oregon and a Graduate Employee in the Special Education
  department. His research interests include Universal Design in post-secondary
  educational settings to support students with disabilities, support for
  students on the autism spectrum attending post-secondary education, and the
  role of self-determination in secondary transition for individuals with
  disabilities.

Hello All,
Looking forward to working with you on this project.
All the best,
Brock

abstract: |Meaningful employment is one of the cornerstones of adult life and has been identified as a critical need for individuals with disabilities (Rogan, Grossi & Gajewski, 2002). Not only does a career promote financial independence, it can also provide an individual with confidence, self-determination, supportive relationships, and engagement within the community. Research has pointed to employment contributing to the development of positive and stable identities, quality of life, and future career success and potential earnings (Levin & Wagner, 2005; Shandra & Hogan, 2008).
Despite this, research consistently demonstrates that employment rates for individuals with disabilities fall significantly below those of individuals without disabilities (Stapleton and Burkhauser 2003; Kaye 2010; OECD 2010; Schur, Kruse, and Blanck 2013; Lauer and Houtenville 2017). Evidence from the Bureau of Labor Statistics (2016) indicates that the percentage of persons with disabilities who are employed was only 17.9 percent as compared to 65.3 percent of persons without disabilities. These employment disparities not only affect the economic well-being of individuals with disabilities (e.g., low income levels and high poverty rates), but also their social inclusion (OECD 2010; WHO/World Bank 2011). The 1990 Americans with Disabilities Act and subsequent 2008 amendments, combined with the 2006 UN convention on the Rights of Persons with Disabilities, is evidence that improving employment opportunities for people with disabilities is an important goal in the United States and around the world (Ameri, Schur, Adya, Bentley, McKay, & Kruse, 2018).
While preparing individuals for employment has been a dominant theme of secondary education and transition for more than two decades (National Collaborative on Workforce and Disability for Youth, 2009; Wehmeyer & Webb, 2012), there has been less emphasis placed on the willingness of employers to hire individuals with disabilities. A primary focus of the employment literature to date has been on strategies to improve employment readiness and the identification of factors that influence employment outcomes for students with disabilities. For example, Rabren, Dunn and Chambers (2002) identified the predictors of postschool employment for individuals with disabilities and much of the research has focused on improving employment readiness skills on behalf of students with disabilities as opposed to focused on employers who should be considered an important stakeholder in this effort.
There have been some studies, however, that have examined the attitudes and perspectives of employers and how they influence employment outcomes for individuals with disabilities. Gilbride Stensrud, Vandergoot and Golden (2003), examined the characteristics of employers who are open to hiring and supporting workers with disabilities and found that even employers who were willing to hire individuals with disabilities still had major concerns maintaining explicit and rigorous hiring guidelines and felt that individuals with disabilities who didn’t meet these criteria would not be considered for competitive employment positions. In another study on employer perspectives, Houtenville and Kalargyrou (2015), compared hiring practices across industries and found that while employers were open to hiring individuals with disabilities, there remained a concern about outward-facing positions and whether or not customers were willing to be served by or interact with individuals with disabilities. Morgan and Alexander (2005), in a comparison study of employers with and without experience hiring individuals with disabilities, found that while most were willing, those with prior experience hiring and working with individuals with disabilities were more comfortable hiring this demographic.
Among other factors, employers’ attitudes toward employees with disabilities is an important influential factor in employment rates for individuals with disabilities (Unger, 2002). While positive employer attitudes may lead to improved employment outcomes for individuals with disabilities, discrimination or other negative attitudes may lead to employment barriers for this population (Livermore & Goodman, 2009). However, as evidenced from the above literature, while there are some studies that have explored employer perspectives toward hiring individuals with disabilities, much of the research exists in niche areas and is both incomplete and out-of-date. Thus, a gap has been identified between the preparedness of individuals with disabilities for competitive integrated employment and the willingness of employers to hire them. Therefore, it is necessary to better understand the perspectives of employers on individuals with disabilities in the workforce. Better understanding of this gap in knowledge will led to better outcomes for individuals with disabilities and more appropriate job matches, as well as leading to more positive perspectives on hiring individuals with disabilities on the part of employers.

  
keywords          : "employment", "employers", "individuals with disabilities", "employment barriers", "hiring" 
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(rio)
library(here)
library(tidyverse)
library(janitor)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load_data}
d <- import(here("data", "employer.sav")) %>%  
            characterize() %>% 
            janitor::clean_names()
```



# Methods
I just copied and pasted info directly into the sections from what Kyle sent, including the two questions Klye said would be worth looking at:

a) What are employers experiences hiring individuals with disabilities?
b) What industries are most open to hiring individuals with disabilities?

Survey participants will be contacted via email and asked to respond to an
online survey (attachment A). Recruitment emails will include a recruitment
statement and a link to the survey, which will be developed using online survey
software called Qualtrics. The survey is being developed by the researchers
conducting the current using previous employer surveys described in prior
studies (Ju et al., 2014; ODEP, 2008) as an impetus for the survey and will
include additional questions and necessary modifications in order to address the
specific research questions described above. Though the survey is still
currently under development by the research team, a draft survey is attached to
this application (attachment B). The research team will submit an IRB amendment
once the final draft of the survey is complete.

## Participants
Our intent is to include relevant employers from across the country, generating
a sample representative of employers across all industries. We will target
individuals who are responsible for or knowledgeable of the hiring practices at
their respective places of employment, though the specifics of this will be
unable to be confirmed. They may be managers, Human Resources representatives,
or others in charge of hiring.
## Material
A researcher-developed survey comprised of questions targeting the hiring
practices and willingness of employers to hire individuals with disabilities
will be used in this study (see attachment A). The survey is anticipated to take
approximately 20 minutes to complete.
## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
Given the exploratory purpose of the study (i.e., to learn more about the
perspectives of employers toward hiring individuals with disabilities), analyses
will be primarily descriptive in nature. Initially, however, we will conduct a
confirmatory factor analysis to validate factor structures of employability
skills, basing the factor structures on a previous study (Ju et al., 2012; Ju et
al., 2014). Next, we will run descriptive statistics for survey items to explore
patterns among survey respondents. Logistic regression analyses will also be
computed to explore whether certain variables are predictive of employers’
responses to individual survey items. Structural equation modeling (e.g.,
exploratory factor analysis) may be used to identify the factor structure of
perceived characteristics of employers willing to hire individuals with
disabilities.

# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Final Paper

## The final project must:

(a) be a reproducible and dynamic APA manuscript produced with R Markdown, via
the {papaja} package and include references to the extant literature; 
(b) be housed on GitHub, with contributions from all authors obvious;
(c) demonstrate moving data from its raw “messy” format to a tidy data format
through the R Markdown file, but not in the final document;
(d) include at least two exploratory data visualizations, and
(e) include at least summary statistics of the data in tables, although fitted
models of any sort are an added bonus (not literally, there are not extra points
for fitting a model).

## The points for the final project are broken down as follows: 
### Writing (abstract, intro, methods, results, discussion, references)

* 30 points(25%) Document is fully reproducible and housed on GitHub 
* 25 points (21%) Demonstrate use of inline code 
* 5 points (4%) Demonstrate tidying messy data 
* 30 points (25%) Two data visualizations 
* 20 points(10 points each) (17%) Production of at least one table (of summary
  statistics or model results)
* 10 points (8%)