---
title             : "EDLD 610 Final Project"
shorttitle        : "Cool Title Name here"

author: 
  - name          : "Brock Rowley"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Behavioral Research & Teaching (BRT)
                    175 Lokey Education 5262 
                    University of Oregon
                    Eugene, OR, 97403-5262"
    email         : "brockr@uoregon.edu"
  - name          : "Kyle Reardon"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"


authornote: |
  Brock Rowley is a Senior Research Associate at Behavioral Research and Teaching (BRT) in the Education Methodolgy, Policy, and Leadership in the Coledge of Education. 
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Kyle Reardon (M.A. Special Education) is a doctoral candidate at the University of Oregon and a Graduate Employee in the Special Education department. His research interests include Universal Design in post-secondary educational settings to support students with disabilities, support for students on the autism spectrum attending post-secondary education, and the role of self-determination in secondary transition for individuals with disabilities.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(rio)
library(here)
library(tidyverse)
library(janitor)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load_data}
d <- import(here("data", "employer.sav")) %>%  
            characterize() %>% 
            janitor::clean_names()
```



# Methods
I just copied and pasted info directly into the sections from what Kyle sent, including the two questions Klye said would be worth looking at:

a) What are employers experiences hiring individuals with disabilities?
b) What industries are most open to hiring individuals with disabilities?

Survey participants will be contacted via email and asked to respond to an
online survey (attachment A). Recruitment emails will include a recruitment
statement and a link to the survey, which will be developed using online survey
software called Qualtrics. The survey is being developed by the researchers
conducting the current using previous employer surveys described in prior
studies (Ju et al., 2014; ODEP, 2008) as an impetus for the survey and will
include additional questions and necessary modifications in order to address the
specific research questions described above. Though the survey is still
currently under development by the research team, a draft survey is attached to
this application (attachment B). The research team will submit an IRB amendment
once the final draft of the survey is complete.

## Participants
Our intent is to include relevant employers from across the country, generating
a sample representative of employers across all industries. We will target
individuals who are responsible for or knowledgeable of the hiring practices at
their respective places of employment, though the specifics of this will be
unable to be confirmed. They may be managers, Human Resources representatives,
or others in charge of hiring.
## Material
A researcher-developed survey comprised of questions targeting the hiring
practices and willingness of employers to hire individuals with disabilities
will be used in this study (see attachment A). The survey is anticipated to take
approximately 20 minutes to complete.
## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Final Paper

Hello Kyle,
Looking forward to working with you on this project. Feel free to invite the person you were talking about in class?? as the third member of our crew. 
All the best,
Brock

## The final project must:

(a) be a reproducible and dynamic APA manuscript produced with R Markdown, via
the {papaja} package and include references to the extant literature; 
(b) be housed on GitHub, with contributions from all authors obvious;
(c) demonstrate moving data from its raw “messy” format to a tidy data format
through the R Markdown file, but not in the final document;
(d) include at least two exploratory data visualizations, and
(e) include at least summary statistics of the data in tables, although fitted
models of any sort are an added bonus (not literally, there are not extra points
for fitting a model).

## The points for the final project are broken down as follows: 
### Writing (abstract, intro, methods, results, discussion, references)

* 30 points(25%) Document is fully reproducible and housed on GitHub 
* 25 points (21%) Demonstrate use of inline code 
* 5 points (4%) Demonstrate tidying messy data 
* 30 points (25%) Two data visualizations 
* 20 points(10 points each) (17%) Production of at least one table (of summary
  statistics or model results)
* 10 points (8%)