---
title             : "EDLD 610 Final Project"
shorttitle        : "Cool running headder here"
author:
  - name          : "Akhila Nekkanti"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Center for Translational Neuroscience University of Oregon 1585 E 13th Ave. Eugene, OR 97403"
    email         : "akhilan@uoregon.edu"
  - name         : "Kyle Reardon"
    affiliation   : "1"
    corresponding : no
  - name          : "Brock Rowley"
    affiliation   : "1"
    corresponding : no
  - name          : "Jeff Gau"
    affiliation   : "1"
    corresponding : no
affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
  Akhila Nekkanti (B.S.) is a doctoral candidate in the Prevention Science
  program at the University of Oregon. Her current research examines the impacts
  of early adversity on children's executive functioning capacities and
  resting-state neural activity. Akhila is co-mentored by Drs. Skowron and Mills
  on her OSLER TL1 project examining the impacts of an intensive, practice-based
  intervention (i.e., PCIT) on children's functional brain organization. Her
  long-term goal is to delineate the type and extent of environmental enrichment
  necessary for enhancing lasting change in self-regulatory capacity in children
  facing early caregiving adversity and trauma.

  Kyle Reardon (M.A. Special Education) is a doctoral candidate at the
  University of Oregon and a Graduate Employee in the Special Education
  department. His research interests include Universal Design in post-secondary
  educational settings to support students with disabilities, support for
  students on the autism spectrum attending post-secondary education, and the
  role of self-determination in secondary transition for individuals with
  disabilities.

  Brock Rowley D.Ed, is a Senior Research Associate I at Behavioral Research and
  Teaching (BRT) and Co-Director of the Admin Licensure Program in the Education
  Methodolgy, Policy, and Leadership (EMPL) in the Coledge of Education at the
  University of Oregon.

  Jeff Gau

abstract: |
  Not only does a career promote financial independence, it can also provide an
  individual with confidence, self-determination, supportive relationships, and
  engagement within the community. A primary focus of the employment literature
  to date has been on strategies to improve employment readiness and the
  identification of factors that influence employment outcomes for students with
  disabilities.Thus, a gap has been identified between the preparedness of
  individuals with disabilities for competitive integrated employment and the
  willingness of employers to hire them. Therefore, it is necessary to better
  understand the perspectives of employers on individuals with disabilities in
  the workforce. Better understanding of this gap in knowledge will led to
  better outcomes for individuals with disabilities and more appropriate job
  matches, as well as leading to more positive perspectives on hiring
  individuals with disabilities on the part of employers.

keywords          : "employment, employers, individuals, disabilities, barriers, hiring"

wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"

classoption       : "man"

output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

# if (!require(psych)) {install.packages("psych")}
# if (!require(likert)) {install.packages("likert")}
# if (!require(maps)) {install.packages("maps")}
# if (!require(RColorBrewer)) {install.packages("RColorBrewer")}
# if (!require(mapproj)) {install.packages("mapproj")}
# if (!require(holepunch)) {remotes::install_github("karthik/holepunch")}

# write_compendium_description(
# package = "EDLD 610 Final",
# description = "Final project for Intro to Data Science")
# write_dockerfile(maintainer = "Brock_Rowley")
# generate_badge()
# build_binder()
# x <- holepunch::get_dependencies(".")
# rem <- lapply(x, remotes:::package2remote)
# rem[[which(x == "pluralize")]]
#install.packages("renv")
#renv::init()
renv::snapshot()
#devtools::install_deps()
#install.packages("curl")
#install.packages("https://github.com/jeroen/curl/archive/master.tar.gz", repos = NULL)
library(devtools)
library(renv)
library(holepunch)
library(papaja)
library(rio)
library(here)
library(tidyverse)
library(janitor)
library(ggplot2)
library(maps)
library(RColorBrewer)
library(mapproj)
library(viridis)
library(psych)
library(likert)
library(shadowtext)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load_data}
d <- import(here("data", "employer.sav")) %>%  
            characterize() %>% 
            janitor::clean_names() 

d_trim <- d %>% 
  select(location_latitude, location_longitude, q3:q6, q7, q8, q25_1:q28_7) %>% 
  filter(complete.cases(.)) %>% 
  rename(loc_lat = location_latitude, 
         loc_long = location_longitude, 
         role = q3, 
         company_size = q5, 
         industry = q6, 
         yrs_company = q7, 
         yrs_role = q8, 
         basic_1 = q25_1, 
         basic_2 = q25_2, 
         basic_3 = q25_3, 
         basic_4 = q25_4, 
         basic_5 = q25_5, 
         basic_6 = q25_6, 
         basic_7 = q25_7, 
         basic_8 = q25_8, 
         higherorder_1 = q24_1, 
         higherorder_2 = q24_2, 
         higherorder_3 = q24_3, 
         higherorder_4 = q24_4, 
         higherorder_5 = q24_5, 
         higherorder_6 = q24_6, 
         persmanage_1 = q26_1, 
         persmanage_2 = q26_2, 
         persmanage_3 = q26_3, 
         persmanage_4 = q26_4, 
         persmanage_5 = q26_5, 
         persmanage_6 = q26_6, 
         persmanage_7 = q26_7, 
         persmanage_8 = q26_8, 
         persmanage_9 = q26_9, 
         persmanage_10 = q26_10, 
         persmanage_11 = q26_11, 
         persmanage_12 = q26_12, 
         interpers_1 = q27_1, 
         interpers_2 = q27_2, 
         interpers_3 = q27_3, 
         interpers_4 = q27_4, 
         interpers_5 = q27_5, 
         interpers_6 = q27_6, 
         interpers_7 = q27_7, 
         attribute_1 = q28_1, 
         attribute_2 = q28_2, 
         attribute_3 = q28_3, 
         attribute_4 = q28_4, 
         attribute_5 = q28_5, 
         attribute_6 = q28_6, 
         attribute_7 = q28_7)
```

```{r heatmap, fig.cap= "Number of surveys collected by state."}

centroids <- import(here("data", "centroids.csv"), 
                    setclass = "tbl_df") %>% 
  mutate(region = tolower(name))

counts_state <- count(d_trim, region = tolower(q4))

centroids <- left_join(centroids, counts_state) %>% 
  mutate(n = ifelse(is.na(n), 0, n))

states <- map_data("state")
md <- left_join(states, counts_state) %>% 
  mutate(states = "state",
         n = ifelse(is.na(n), 0, n))

ggplot(md, aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n),
               color = "gray40") +
  geom_shadowtext(aes(x = longitude, y = latitude, label = n), 
            data = filter(centroids, 
                          state != "AK" & 
                          state != "HI" & 
                          state != "PR"),
            inherit.aes = FALSE,
            col = 'lightsteelblue') +
  coord_map() +
    labs(x = NULL, 
         y = NULL, 
         title = "Employer Survey Responses by State") + 
  scale_fill_viridis(
    option = "inferno",
    name = "Number of survey responses\n",
    direction = 1) +
  theme_void() +
  theme(legend.position = "bottom",
        legend.key.width = unit(2, "cm"),
        plot.background = element_rect(fill = 'gray20', colour = 'gray20'),
        plot.title = element_text(color = "white", size = 20),
        legend.text = element_text(color = "gray40"),
        legend.title = element_text(color = "white"))
```

```{r likert_plots}

#Q24= higherorder, 1= solve probs; 2= seek help, 3= critical thinking, 4=creative thinking, 5=impact of decisions, 6= employ research

#View(d_trim)

d_trim <- d_trim %>% 
  drop_na() %>% 
  mutate_at(vars("basic_1":"attribute_7"), 
            funs(factor(.,
                               levels = c(
                                   "Not at all",
                              "Somewhat",
                              "Very",
                              "Extremely"),
                              ordered = TRUE)))

basic <- d_trim %>% 
  select(contains("basic"))

higherorder <- d_trim %>% 
  select(contains("higherorder"))

persmanage <- d_trim %>% 
  select(contains("persmanage"))

##################### finish with remaining variables


#levels(d_trim$higherorder_1)  #check that it worked

higherorder_result = likert(higherorder)
summary(higherorder_result)
plot(higherorder_result, type = "bar")

#q24_plot <- d_trim %>% 
#  group_by(industry) %>% 
#  summarize()

```

# Introduction

Meaningful employment is one of the cornerstones of adult life and has been
identified as a critical need for individuals with disabilities
[@rogan2002vocational]. Not only does a career promote financial independence,
it can also provide an individual with confidence, self-determination,
supportive relationships, and engagement within the community. Research has
pointed to employment contributing to the development of positive and stable
identities, quality of life, and future career success and potential earnings
[@wagner2005after; @shandra2008school].

Despite this, research consistently demonstrates that employment rates for
individuals with disabilities fall significantly below those of individuals
without disabilities [@stapleton2003contrasting; @kaye2010impact;
@schur2013people]. Evidence from the @dohm2007occupational indicates that the
percentage of persons with disabilities who are employed was only 17.9 percent
as compared to 65.3 percent of persons without disabilities. These employment
disparities not only affect the economic well-being of individuals with
disabilities (e.g., low income levels and high poverty rates), but also their
social inclusion @krahn2011world. The 1990 Americans with Disabilities Act and
subsequent 2008 amendments, combined with the 2006 UN convention on the Rights
of Persons with Disabilities, is evidence that improving employment
opportunities for people with disabilities is an important goal in the United
States and around the world [@ameri2018disability].

While preparing individuals for employment has been a dominant theme of
secondary education and transition for more than two decades
[@wehmeyer2012introduction], there has been less emphasis placed on the
willingness of employers to hire individuals with disabilities. A primary focus
of the employment literature to date has been on strategies to improve
employment readiness and the identification of factors that influence employment
outcomes for students with disabilities. For example, @rabren2002predictors
identified the predictors of postschool employment for individuals with
disabilities and much of the research has focused on improving employment
readiness skills on behalf of students with disabilities as opposed to focused
on employers who should be considered an important stakeholder in this effort.

There have been some studies, however, that have examined the attitudes and
perspectives of employers and how they influence employment outcomes for
individuals with disabilities. @gilbride2003identification examined the
characteristics of employers who are open to hiring and supporting workers with
disabilities and found that even employers who were willing to hire individuals
with disabilities still had major concerns maintaining explicit and rigorous
hiring guidelines and felt that individuals with disabilities who didn’t meet
these criteria would not be considered for competitive employment positions. In
another study on employer perspectives, @houtenville2015employers, compared
hiring practices across industries and found that while employers were open to
hiring individuals with disabilities, there remained a concern about
outward-facing positions and whether or not customers were willing to be served
by or interact with individuals with disabilities. @morgan2005employer, in a
comparison study of employers with and without experience hiring individuals
with disabilities, found that while most were willing, those with prior
experience hiring and working with individuals with disabilities were more
comfortable hiring this demographic.

Among other factors, employers’ attitudes toward employees with disabilities is
an important influential factor in employment rates for individuals with
disabilities [@unger2002employers]. While positive employer attitudes may lead
to improved employment outcomes for individuals with disabilities,
discrimination or other negative attitudes may lead to employment barriers for
this population [@livermore2009review]. However, as evidenced from the above
literature, while there are some studies that have explored employer
perspectives toward hiring individuals with disabilities, much of the research
exists in niche areas and is both incomplete and out-of-date. Thus, a gap has
been identified between the preparedness of individuals with disabilities for
competitive integrated employment and the willingness of employers to hire them.
Therefore, it is necessary to better understand the perspectives of employers on
individuals with disabilities in the workforce. Better understanding of this gap
in knowledge will led to better outcomes for individuals with disabilities and
more appropriate job matches, as well as leading to more positive perspectives
on hiring individuals with disabilities on the part of employers.

# Methods
I just copied and pasted info directly into the sections from what Kyle sent, including the two questions Klye said would be worth looking at:

a) What are employers experiences hiring individuals with disabilities?
b) What industries are most open to hiring individuals with disabilities?

Survey participants will be contacted via email and asked to respond to an
online survey (attachment A). Recruitment emails will include a recruitment
statement and a link to the survey, which will be developed using online survey
software called Qualtrics. The survey is being developed by the researchers
conducting the current using previous employer surveys described in prior
studies [@ju2014employability; @domzal2008survey] as an impetus for the survey and will
include additional questions and necessary modifications in order to address the
specific research questions described above. Though the survey is still
currently under development by the research team, a draft survey is attached to
this application (attachment B). The research team will submit an IRB amendment
once the final draft of the survey is complete.

## Participants
Our intent is to include relevant employers from across the country, generating
a sample representative of employers across all industries. We will target
individuals who are responsible for or knowledgeable of the hiring practices at
their respective places of employment, though the specifics of this will be
unable to be confirmed. They may be managers, Human Resources representatives,
or others in charge of hiring.
## Material
A researcher-developed survey comprised of questions targeting the hiring
practices and willingness of employers to hire individuals with disabilities
will be used in this study (see attachment A). The survey is anticipated to take
approximately 20 minutes to complete.
## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
Given the exploratory purpose of the study (i.e., to learn more about the
perspectives of employers toward hiring individuals with disabilities), analyses
will be primarily descriptive in nature. Initially, however, we will conduct a
confirmatory factor analysis to validate factor structures of employability
skills, basing the factor structures on a previous study (Ju et al., 2012; Ju et
al., 2014). Next, we will run descriptive statistics for survey items to explore
patterns among survey respondents. Logistic regression analyses will also be
computed to explore whether certain variables are predictive of employers’
responses to individual survey items. Structural equation modeling (e.g.,
exploratory factor analysis) may be used to identify the factor structure of
perceived characteristics of employers willing to hire individuals with
disabilities.

# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Final Paper

## The final project must:

(a) be a reproducible and dynamic APA manuscript produced with R Markdown, via
the {papaja} package and include references to the extant literature; 
(b) be housed on GitHub, with contributions from all authors obvious;
(c) demonstrate moving data from its raw “messy” format to a tidy data format
through the R Markdown file, but not in the final document;
(d) include at least two exploratory data visualizations, and
(e) include at least summary statistics of the data in tables, although fitted
models of any sort are an added bonus (not literally, there are not extra points
for fitting a model).

## The points for the final project are broken down as follows: 
### Writing (abstract, intro, methods, results, discussion, references)

* 30 points(25%) Document is fully reproducible and housed on GitHub 
* 25 points (21%) Demonstrate use of inline code 
* 5 points (4%) Demonstrate tidying messy data 
* 30 points (25%) Two data visualizations 
* 20 points(10 points each) (17%) Production of at least one table (of summary
  statistics or model results)
* 10 points (8%)